---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
```

## botornot

An R package for classifying Twitter accounts as `bot or not`.

## Features

Uses machine learning to classify Twitter accounts as bots or not bots. 
The model is 94% accurate. It is slightly better at classifying not bots than 
classifying bots (low type I error).

## Install

Install from Github.

```{r, eval=FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("mkearney/botornot")
```

## Usage

There's one function `botornot()`. Give it a vector of screen names, user IDs, or data frames returned by [rtweet](http://rtweet.info).

```{r}
## load package
library(botornot)

## select users
users <- c("realdonaldtrump", "netflix_bot",
  "kearneymw", "dataandme", "hadleywickham",
  "ma_salmon", "juliasilge", "tidyversetweets")

## get botornot estimates
data <- botornot(users)

## arrange by prob ests
data[order(data$prob_bot), ]
```
